Contract Orchestration for OCaml \\ Progress Report

### 2022-09-20 reports/2022-09-06/COOC-report.tex
update report and lib

We have made progress on several points in the contract.
\begin{itemize}
\item A type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain. The work has been presented and published at APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}. 
\item The typed Tezos API is completely implemented.
\item extend Contract modules to contract specifications that include pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
\end{itemize}

@@

We plan to 
\begin{itemize}
\item continuous our teaching activities (the blockchain course, a seminar on the topic in the winter semester).
\item implement the converter for the Assertiom contract (for Tezos and Ethereum). 
\item package the document to a paper about assertion contract to a conference paper.
\item implement code generation for contract modules; 
\item 
\item design and implement a checker for contract specifications based on Michelsym.
\end{itemize}

>>>>

We have made progress on several points in the contract.
\begin{itemize}
\item A type-safe interaction between an Ocaml program and Michelson smart contracts on the Tezos blockchain. The work was presented and published at APLAS 2021 conference \cite{DBLP:conf/fc/ThiemannAplas21}. 
\item The initial state of work on Contract modules was presented and published at the Formal Methods for Blockchains (FMBC 2021) workshop \cite{DBLP:conf/fc/ThiemannFmbc21}.

\item The typed Tezos API is completely implemented.
\item a symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
\end{itemize}

@@

We plan to 
\begin{itemize}
\item continuous our teaching activities (the blockchain course, a seminar on the topic in the winter semester).
\item implement the converter for the Assertiom contract (for Tezos and Ethereum). 
\item package the document to a paper about assertion contract to a conference paper.
\item implement code generation for contract modules; 
\item implement a checker for contract specifications based on Michelsym.
\end{itemize}
